---
title: "Report"
author: "Tom Mushkat"
date: "8/16/2021"
output:
  html_document:
    code_folding: hide
    df_print: kable
    results: hide
    theme: readable
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, here, skimr, anytime, car, effectsize, gmodels, apaTables, psych, rcompanion, ResourceSelection, lmtest, faraway, estimatr, tidymodels, hdm)

continuousOutliers <- function(data, lowerBound = 3, upperBound = 3){
  
  # This function takes a vector, and replace observations that are smaller or bigger than the lower/upper bounds * standard deviations with NA
  
  Mean   <- mean(data, na.rm = TRUE)
  SD     <- sd(data, na.rm = TRUE)
  High   <- Mean + upperBound * SD # Upper Range  
  Low    <- Mean - lowerBound * SD # Lower Range
  Final  <- ifelse(data > High | data < Low, NA, data)
  
  return(Final)
  
}

#   Male <- read_csv(here('Data/male.csv'))
#   Female <- read_csv(here('Data/female.csv'))
# 
# Male1 <- Male[3:nrow(Male), ]
# Male2 <- Male1 %>%
#   drop_na(ID)
# 
# Female1 <- Female[3:nrow(Female), ]
# Female2 <- Female1 %>%
#   drop_na(ID)
# 
#  originalData <- rbind(Male2, Female2)

# write.csv(Data, 'cleanDataUpdated.csv')
# Data <- read_csv(here('Data/cleanDataUpdated.csv'))
Data <- read_csv(here('Data/cleanData.csv'))
# Data <- Data %>%
#   filter(Sex == 'Female')
Data$cleanDuration <- continuousOutliers(Data$Duration)
Data <- Data %>% 
  filter(is.na(cleanDuration) == FALSE) 
  filter(Unclear == 'Clear')
```

```{r, warning=FALSE, message=FALSE}
Data$Condition <- ifelse(is.na(Data$Know) == T, 'knowCondition', 'dontKnowCondition')

# Data <- Data %>% 
#   mutate(dontKnow = as.numeric(ifelse(dontKnowFirst == '1 (False)', 1, 
#                                 ifelse(dontKnowFirst == '7 (True)', 7, dontKnowFirst))),
#          Know1 = as.numeric(ifelse(Know == '1 (False)', 1, 
#                                 ifelse(Know == '7 (True)', 7, Know))),
#          DV = ifelse(is.na(Know1) == T, dontKnow, Know1))
```



```{r, warning=FALSE, message=FALSE}
Data$DV1 <- rowSums(cbind(Data$`allPluse2[, 2]`, Data$`allPluse2[, 3]`, Data$`allPluse2[, 4]`,
                          Data$`allPluse2[, 5]`, Data$`allPluse2[, 6]`, Data$`allPluse2[, 7]`)) / 6
Data$DV2 <- ifelse(Data$`allPluse2[, 2]` == 0 | Data$`allPluse2[, 3]` == 0 | Data$`allPluse2[, 4]` == 0 |
                          Data$`allPluse2[, 5]` == 0 | Data$`allPluse2[, 6]` == 0 | Data$`allPluse2[, 7]` == 0, 'dontConfirm', 'Confirm')
# Data <- Data %>% 
#   mutate(dontKnow = as.numeric(ifelse(dontKnowFirst == '1 (False)', 1, 
#                                 ifelse(dontKnowFirst == '7 (True)', 7, dontKnowFirst))),
#          Know1 = as.numeric(ifelse(Know == '1 (False)', 1, 
#                                 ifelse(Know == '7 (True)', 7, Know))),
#          DV = ifelse(is.na(Know1) == T, dontKnow, Know1))
```


```{r, warning=FALSE, message=FALSE}

Data$R_Intellectualhumility_DO_Q275 <- 8 - Data$Intellectualhumility_DO_Q275
Data$R_Intellectualhumility_DO_Q279 <- 8 - Data$Intellectualhumility_DO_Q279
Data$R_Intellectualhumility_DO_Q280 <- 8 - Data$Intellectualhumility_DO_Q280


Intelectual <- as.matrix(cbind(cbind(Data$R_Intellectualhumility_DO_Q275,
                                     Data$Intellectualhumility_DO_Q276,
                                     Data$Intellectualhumility_DO_Q277,
                                     Data$Intellectualhumility_DO_Q278,
                                     Data$R_Intellectualhumility_DO_Q279,
                                     Data$R_Intellectualhumility_DO_Q280)))
# psych::alpha(Intelectual)

Data$intellectualhumility <- rowMeans(cbind(Data$R_Intellectualhumility_DO_Q275,
                                     Data$Intellectualhumility_DO_Q276,
                                     Data$Intellectualhumility_DO_Q277,
                                     Data$Intellectualhumility_DO_Q278,
                                     Data$R_Intellectualhumility_DO_Q279,
                                     Data$R_Intellectualhumility_DO_Q280))
```

# All sample
## Rate of confirming (DV1) histogram by condition
```{r, warning=FALSE, message=FALSE}
Data %>% 
  ggplot(aes(x = DV1)) + 
  geom_histogram() + 
  facet_grid(~Condition) + 
  xlab('Rate of confirming') + ylab('Frequency')
```

## Descriptive statistics of the Rate of confirming (DV1), Mann-Whitney test and box plot -  by condition
```{r, warning=FALSE, message=FALSE}

Data %>% 
  group_by(Condition) %>% 
  summarise(Mean = round(mean(DV1), 2),
            SD   = round(sd(DV1), 2),
            Median = round(median(DV1), 2),
            N = length(DV1))

# varTest <- var.test(DV1 ~ Condition, data = Data)
# trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
# Model <- t.test(DV1 ~ Condition, var.equal = trueVarTest, data = Data)
# Model
wilcox.test(DV1 ~ Condition, correct = FALSE, data = Data)
# effectsize(Model)

boxplot(Data$DV1 ~ Data$Condition,
  ylab = "Rate of confirming",
  main = 'Condition'
)


```

## Chi-Square frequency of at list single non-confirming (DV2) by condition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV2, Data$Condition, chisq = T, format = 'SPSS')
```


# Only do not know condition
## Rate of confirming (DV1) histogram by condition
```{r, warning=FALSE, message=FALSE}
dataDontKnwo <- Data %>%
  filter(FL_5_DO_Dontknow == 1) %>%
  mutate(newCondition = ifelse(dontKnowFirst == "I don't know", 'dontKnow', 'Know'))

dataDontKnwo %>% 
  ggplot(aes(x = DV1)) + 
  geom_histogram() + 
  facet_grid(~newCondition) + 
  xlab('Rate of confirming') + ylab('Frequency')
```

## Descriptive statistics of the Rate of confirming (DV1), Mann-Whitney test and box plot -  by condition
```{r, warning=FALSE, message=FALSE}

dataDontKnwo %>% 
  group_by(newCondition) %>% 
  summarise(Mean = round(mean(DV1), 2),
            SD   = round(sd(DV1), 2),
            Median = round(median(DV1), 2),
            N = length(DV1))

# varTest <- var.test(DV1 ~ Condition, data = Data)
# trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
# Model <- t.test(DV1 ~ Condition, var.equal = trueVarTest, data = Data)
# Model
wilcox.test(DV1 ~ newCondition, correct = FALSE, data = dataDontKnwo)
# effectsize(Model)

boxplot(dataDontKnwo$DV1 ~ dataDontKnwo$newCondition,
  ylab = "Rate of confirming",
  main = 'Condition'
)


```

## Chi-Square frequency of at list single non-confirming (DV2) by answering 'dont know'
```{r, warning=FALSE, message=FALSE}
CrossTable(dataDontKnwo$DV2, dataDontKnwo$newCondition, chisq = T, format = 'SPSS')
```
